This report has presented the analysis, design, and implementation of CyberScope, an integrated platform for automated web application security assessment. We described the adopted development methodology, the system architecture, the orchestration of external scanning tools, and the frontend dashboard used for visualization and reporting. The work demonstrates how heterogeneous components—backend services, a Python-based scanning engine, dynamic crawlers, and AI-assisted analysis—can be combined into a coherent, extensible solution.

The implementation validated the proposed architecture: the backend provides reliable orchestration and persistence of scan results, the scanning engine automates interactions with established security tools, and the frontend offers clear visualization and filtering of findings. Key design choices such as modularity, use of standard tooling (Node.js, Prisma, PostgreSQL, React), and the adoption of an orchestration layer (HexStrike AI) made the system easier to extend and maintain.

Evaluation focused on correctness, scalability and usability. The pipeline successfully aggregates heterogeneous outputs, normalizes and deduplicates findings, and produces structured reports that facilitate prioritization and remediation. Performance considerations and fault-tolerance mechanisms were discussed to ensure scans can run concurrently and recover from partial failures. Usability improvements in the dashboard and report generation help stakeholders rapidly understand the security posture of target applications.

Future work includes broadening tool coverage, improving the AI analysis models and integration (e.g., richer local models or external engines), adding role-based access control and audit trails, and hardening the orchestration layer for large-scale distributed scans. Additional validation in realistic production scenarios and user studies would further strengthen the platform's maturity and operational readiness.

In summary, CyberScope provides a pragmatic and extensible foundation for automated web application security assessment. The project combines proven open-source tools, a maintainable development stack, and automation patterns that together enable efficient, repeatable security testing and reporting for modern web applications.