\thispagestyle{plain}
\begin{center}
    {\Large \textbf{Dedications}}
\end{center}

\vspace{0.6cm}

First and foremost, I thank \textbf{Allah} for choosing me among thousands to face this trial, which has made me more patient, wiser, and stronger. Despite the back injury that has challenged me for more than a year and a half, during which I could barely sit to work, all praise be to Allah for His guidance and strength.

\vspace{0.18cm}

To my beloved family, who replaced my physical pain with their unwavering support, love, and care:

\vspace{0.18cm}

To \textbf{Anissa, my mother}, whose devotion knew no bounds---checking on my condition and illness every single day throughout this difficult period. Your constant care has been my healing.

\vspace{0.12cm}

To \textbf{Hassen, my father}, who dedicated himself entirely to ensuring my comfort, doing everything possible to ease my burden. Your sacrifices have not gone unnoticed.

\vspace{0.12cm}

To \textbf{Iskander}, who became my backbone and eternal supporter when my own failed me. You carried me through the darkest moments.

\vspace{0.12cm}

To \textbf{Sabri}, from whom I drew power and strength when mine was depleted. Your presence gave me energy to continue.

\vspace{0.12cm}

To \textbf{Naktel}, the youngest among us, who brought joy and happiness into days filled with pain. Your light brightened my path.

\vspace{0.18cm}

Every line of this report was written through immense pain and is dedicated to all of you. Your love transformed my struggle into strength, and your faith in me made this achievement possible.

\vspace{0.5cm}

\hfill \textit{Alhamdulillahi rabbil alameen.}