\hspace*{1.2cm} In recent years, the rapid evolution of web technologies has significantly transformed the development and deployment of modern applications. Web applications have become increasingly dynamic, interactive, and complex, relying heavily on client-side rendering and continuous communication with backend services. While these advancements have enhanced user experience, they have also expanded the attack surface and introduced new security challenges.

Web application security has become a critical concern for organizations. Vulnerabilities such as SQL injection, cross-site scripting (XSS), and authentication flaws remain among the most exploited attack vectors, as highlighted by the OWASP Top 10. These vulnerabilities can lead to severe consequences, including data breaches, financial losses, and reputational damage.

To mitigate these risks, various security scanning tools have been developed, including solutions such as Nikto, OWASP ZAP, and Burp Suite. Although these tools provide valuable capabilities, they exhibit significant limitations. In particular, traditional scanners struggle to effectively analyze modern Single Page Applications (SPAs), where content is dynamically generated through JavaScript. Furthermore, they often produce redundant or low-priority findings, making vulnerability analysis more complex and less efficient.

In this context, there is a growing need for more intelligent and adaptive security auditing systems capable of handling modern web architectures while improving detection accuracy and result relevance.

To address these challenges, this project introduces \textbf{CyberScope}, an automated web application security auditing system designed to detect and analyze vulnerabilities through intelligent orchestration and advanced automation techniques. The proposed system integrates multiple security tools within a unified pipeline and enhances their capabilities through a browser-based crawling agent capable of exploring dynamic applications. In addition, an AI-driven correlation engine is employed to normalize, deduplicate, and prioritize detected vulnerabilities, providing more meaningful and actionable insights.

The objective of this work is to design and implement a comprehensive and efficient security auditing platform that improves vulnerability detection coverage  and adapts to the complexity of modern web environments.